Demonstration of matching route networks

### 2024-02-13 r/demo.qmd
More demos

>>>>

We can merge the two datasets using the `rnet_merge` function from the `stplanr` package:

```{r}
rnet_merged = rnet_merge(rnet_x, rnet_y["flow"], dist = 9, segment_length = 20, funs = list(flow = sum))
sum(rnet_merged$flow * sf::st_length(rnet_merged$geometry), na.rm = TRUE)
sum(rnet_y$flow * sf::st_length(rnet_y$geometry), na.rm = TRUE)
```

We can tweak the parameters:

```{r}
rnet_merged = rnet_merge(rnet_x, rnet_y["flow"], dist = 9, segment_length = 20, funs = list(flow = sum), sum_flows = FALSE)
sum(rnet_merged$flow * sf::st_length(rnet_merged$geometry), na.rm = TRUE)
```

With the new implementation:

# With the Princes Street example

```{r}
library(sf)
library(rnetmatch)
x <- read_sf(system.file("extdata", "princes_street_minimal_x_1.geojson", package = "rnetmatch")) |>
  sf::st_transform(27700)
x = x[3, ]
x
y <- read_sf(system.file("extdata", "princes_street_minimal.geojson", package = "rnetmatch")) |>
  sf::st_transform(27700)
y = y[2:3, ]

plot(x$geometry, col = "grey", lwd = 5)
plot(y$geometry, add = TRUE, lwd = 2)

matches <- rnetmatch::rnet_match(x, y, dist_tolerance = 10, angle_tolerance = 5)

rnet_aggregate_intensive(x, y, matches, value)
rnet_aggregate_extensive(x, y, matches, value)
```

For the full example:

```{r}
x <- read_sf(system.file("extdata", "princes_street_minimal_x_1.geojson", package = "rnetmatch")) |>
  sf::st_transform(27700)
x
y <- read_sf(system.file("extdata", "princes_street_minimal.geojson", package = "rnetmatch")) |>
  sf::st_transform(27700)

my = tm_shape(y) + tm_lines("value", lwd = 2)
mx = tm_shape(x) + tm_lines(lwd = 5, col = "grey")
mx + my

matches <- rnetmatch::rnet_match(x, y, dist_tolerance = 10, angle_tolerance = 5)

mx_intensive = rnet_aggregate_intensive(x, y, matches, value)
mx_extensive = rnet_aggregate_extensive(x, y, matches, value)
mx_intensive
mx_extensive
mx_intensivej = dplyr::left_join(x, mx_intensive |> dplyr::rename(id = i))
mx_extensivej = dplyr::left_join(x, mx_extensive |> dplyr::rename(id = i))

my + tm_shape(mx_intensivej) + tm_lines("value", lwd = 2)
my + tm_shape(mx_extensivej) + tm_lines("value", lwd = 2)
```
